### 2015-01-22 publishing/plos_template.tex

Printable micropipette designs can be found on 3D-part sharing websites.
While existing designs mayb require only pen springs, a gasket made from a balloon, and tape, none allow adjustment to know volumes.
We present a pipette constructed from 3D printed parts that allows a 1 mL syringe to be actuated to an adjustable volume.
The scale marks on the syringe can be used to adjust the dispensed volume accurately without calibrating with a scale.

@@

\begin{figure}
\includegraphics[scale=0.4]{figure-images/rendering-assembly4.png} % take image out for final manuscript
\caption{
{\bf CAD rendering of printable parts.}  Three parts are printed: the body, plunger shaft, and luer-lock adaptor for pipette tips.
}
\label{CAD-render-figure}
\end{figure}

>>>>

Printable micropipette designs can be found on 3D-part sharing websites.
While existing designs may require only pen springs, a gasket made from a balloon, and tape, none allow adjustment to know volumes.
We present a pipette constructed from 3D printed parts that allows a 1 mL syringe to be actuated to an adjustable volume.
The scale marks on the syringe can be used to adjust the dispensed volume accurately without calibrating with a scale.

@@

\begin{figure}
\includegraphics[scale=0.4]{figure-images/rendering-assembly4.png} % take image out for final manuscript
\caption{
{\bf CAD rendering of printable parts.}  Three parts are printed: the body, plunger shaft, and luer-lock adapter for pipette tips.
}
\label{CAD-render-figure}
\end{figure}
